Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-29 paper/letter.tex
Nico's comments

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo Calculation using the
\texttt{emcee} implementation.
We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
$\theta$ using $XX$ steps.
The results are summarized in Figure \ref{emceeresults}. 
From this model we find that the fiducial parameters that could
explain the broad features in \tol\ are $V_{\rm max}=348^{+75}_{-48}$
km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, $\log_{10} T/\mathrm
{K} = 4.27^{+0.11}_{-0.18}$ and  $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

@@

>>>>

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo Calculation using the
\texttt{emcee} implementation.
We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
$\theta$ using $500$ steps with $24$ walkers for a total of $12000$
points.
The results are summarized in Figure \ref{emceeresults}. 
From this model we find that the fiducial parameters that could
explain the broad features in \tol\ are $V_{\rm max}=348^{+75}_{-48}$
km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, $\log_{10} T/\mathrm
{K} = 4.27^{+0.11}_{-0.18}$ and  $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

@@

\section*{The Outflow Model}
The galaxy outflow model is a highly sucessful framework to fit
and interprete \lya\ line observations.
